
 \begin{thebibliography}{1}
   
      \addcontentsline{toc}{section}{Livros} % faz aparecer no sumário
      \section*{Livros}
      
      
           \bibitem{jb}
   Butcher, J. C.;
   \textit{Numerical Methods for Ordinary Differential Equations}, Second Edition,
   Wiley, 2008.
   
      \bibitem{dnr}
   Dascalescu, S.; Nastasescu, C.; Raianu, S.;
   \textit{Hopf Algebras: an introduction}, 
   Marcel Dekker 2001.
   
           \bibitem{var}
   Gracia-Bondía, J. M.; Várilly, J. C.; Figueroa, H.;
   \textit{Elements of Noncommutative Geometry}
   Birkhäuser, 2001.
   
       \bibitem{gyz}
   Gross, J. L.; Yellen, J.; Zhang, P.;
   \textit{Handbook of Graph Theory}, Second Edition,
   CRC, 2014.    
   
        \bibitem{hnw}
   Hairer, E.; Nørsett, S. P.; Wanner, G.;
   \textit{Solving Ordinary Differential Equations I - Nonstiff Problems}, Second Revised Edition,
   Springer, 2008.  
   
       \bibitem{nj}
   Jacobson, N.;
   \textit{Lie Algebras},
   Dover, 1979.
   
   \bibitem{ak} 
   Kirillov, A.;
   \textit{An Introduction to Lie Groups and Lie Algebras},
   Cambridge, 2008. 

     \bibitem{rad} 
   Radford, D. E.;
   \textit{Hopf Algebras}, 
   World Scientific 2012.
  
  
   \addcontentsline{toc}{section}{Dissertações e teses} % faz aparecer no sumário
      \section*{Dissertações e teses}
      
      \bibitem{sch} 
   Schutzer, W.;
   \textit{Álgebras de Lie, álgebras de Hopf e grupos quânticos}, 
   Dissertação de mestrado, USP, 1996.
   Disponível em: \\ \texttt{http://www.dm.ufscar.br/profs/waldeck/tese.pdf}.
      
   \bibitem{mat} 
   Teixeira, M. M.; 
   \textit{Extensões de álgebras obtidas a partir de álgebras de Hopf}, 
   Dissertação de mestrado, UFSC, 2011.
   Disponível em: \\ \texttt{https://repositorio.ufsc.br/xmlui/handle/123456789/95887}.
  

   
    \addcontentsline{toc}{section}{Artigos} % faz aparecer no sumário
      \section*{Artigos}
      
     \bibitem{cb}
  Brouder, C.;
  \textit{Runge-Kutta methods and renormalization},
 Eur. Phys. J. C (2000), 521-534. Disponível em: \\ \texttt{http://link.springer.com/article/10.1007\%2Fs100529900235\#page-2} ou em \texttt{http://arxiv.org/pdf/hep-th/9904014.pdf}.
  
  \bibitem{cefm}
   Calaque, D.; Ebrahimi-Fard, K.; Manchon, D.;
   \textit{Two interacting Hopf algebras of trees},
   Advances in Applied Mathematics 47 (2011) 282-308.
   Disponível em \texttt{http://arxiv.org/abs/0806.2238}.
   
   \bibitem{chv}
  Chartier, P.; Hairer, E.; Vilmart, G.;
   \textit{Algebraic structures of B-series},
   Found. Comput. Math. 10(7) (2010) 407-427.
   Disponível em: \\ \texttt{http://www.unige.ch/~vilmart/publications.html}.
   
     \bibitem{ck} 
  Connes, A.; Kreimer, D.;
  \textit{Hopf Algebras, Renormalization and Noncommutative Geometry},
  Comm. Math. Phys (1998), 203-242. Disponível em: \\ \texttt{http://arxiv.org/abs/hep-th/9808042}.
 
   \bibitem{lf} 
  Foissy, L.; 
  \textit{An introduction to Hopf algebras of trees},
  Preprint, 2013. Disponível em: \\ \texttt{http://loic.foissy.free.fr/pageperso/preprint3.pdf}.
  
     \bibitem{gar} 
  Garrett, P.;
   \textit{Poincaré-Birkhoff-Witt theorem}, 
   2011. Disponível em: \\
   \texttt{http://www.math.umn.edu/\~garrett/m/algebra/pbw.pdf}.
   
   \bibitem{gl}
 Grossman, R.; Larson, R. G.;
  \textit{Hopf-algebraic structures of families of trees},
  J. Algebra, 126 (1989), 184-210. Disponível em: \\ \texttt{http://arxiv.org/abs/0711.3877}.
  
 \bibitem{mh}
  Hoffman, M. E.;
  \textit{Combinatorics of Rooted Trees and Hopf Algebras},
  Trans. Amer. Math. Soc. 355 (2003), 3795-3811. Disponível em: \\ \texttt{http://www.ams.org/journals/tran/2003-355-09/S0002-9947-03-03317-8/}.
 
   \bibitem{fp}
  Panaite, F.;
  \textit{Relating the Connes-Kreimer and Grossman-Larson Hopf algebras built on rooted trees}
  Letters in Mathematical Physics 51 (2000), 211-219. Disponível em: \\ \texttt{http://arxiv.org/abs/math/0003074}.
  
 \end{thebibliography}

